---
title: "Hood River Spring Chinook and Steelhead Forecasting Models"
author: "Mark Roes"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE, fig.height = 4, fig.width = 6.5, dpi = 300)
options(scipen = 999)
source('R/package_load.r')

package_load(package_list = c("plyr","tidyverse", "janitor", "lubridate", "dataRetrieval", "brms", "readxl", "here", "flextable"))
set.seed(1571)
```

```{r load-data, results = "hold"}
load(file = "R/prediction_year.rda")

ad_count = read_excel('data input/Abundance/AbundanceData.xlsx',
                       sheet = 'Adult') %>%
  janitor::clean_names()

smolt_count = read_excel('data input/Abundance/AbundanceData.xlsx',
                          sheet = 'Smolt') %>%
   janitor::clean_names()

npgo = read_csv('data input/Environmental/NPGO.csv') %>%
  janitor::clean_names()

if(!(prediction_year %in% unique(c(npgo$year, max(npgo$year+1))))){
    print("Warning: Either the NPGO data has not been updated, or the prediction_year was not entered correctly. Results may not be valid.")
}

if(prediction_year == max(npgo$year+1)){
  npgo = npgo %>%
    bind_rows(tibble(year = prediction_year))
}
#Load in Tucker bridge gage flow

tucker_flow = readNWISdv("14120000", "00060", "1987-01-01", Sys.Date()) %>%
  dplyr::select(Date, X_00060_00003) %>%
  dplyr::rename(cfs_daily = X_00060_00003) %>%
  janitor::clean_names() %>%
  mutate(year = year(date),
         month = month(date)) %>%
  group_by(year) %>%
  dplyr::summarise(min_flow_yr = min(cfs_daily)) %>%
  ungroup()
```

```{r wst-dat}
wst_env_dat = npgo %>%
              filter(month == 5 | is.na(month)) %>%
  left_join(tucker_flow)

wst_ages = read_excel('data input/Abundance/AgeData.xlsx',
                      sheet = 'NOR WSTHD scales') %>%
  janitor::clean_names() %>%
  pivot_longer(2:last_col(1)) %>%
  dplyr::mutate(fresh = substr(name,2,2),
                salt = substr(name,4,4))

wst_props = bind_rows(wst_ages %>%
                        dplyr::mutate(age = as.numeric(fresh) + as.numeric(salt)) %>%
                        group_by(age, year) %>%
                        dplyr::summarise(prop_yr = age/total) %>%
                        ungroup() %>%
                        group_by(age) %>%
                        dplyr::summarise(prop = mean(prop_yr)) %>%
                        ungroup() %>%
                        dplyr::mutate(type = 'age',
                                      class = as.factor(age)) %>%
                        dplyr::select(type, class, prop),
                        # age_summary %>%
                        # #proportions by age
                        # filter(run == "WSTHD") %>%
                        # pivot_longer(cols = names(.)[-c(1,2,9)]) %>%
                        # dplyr::mutate(type = 'age',
                        #               class = substr(name,5,5),
                        #               prop_yr = value/total) %>%
                        # group_by(type, class) %>%
                        # dplyr::summarise(prop = mean(prop_yr)) %>%
                        # ungroup(),
                      #proportions by fresh
                      wst_ages %>%
                        group_by(year, total, fresh) %>%
                        dplyr::summarise(prop_fresh_yr = sum(value)/total) %>%
                        ungroup() %>%
                        distinct() %>%
                        group_by(fresh) %>%
                        dplyr::summarise(prop = mean(prop_fresh_yr)) %>%
                        ungroup() %>%
                        mutate(type = 'fresh') %>%
                        rename(class = fresh),
                      #proportions by salt
                      wst_ages %>%
                        group_by(year, total, salt) %>%
                        dplyr::summarise(prop_salt_yr = sum(value)/total) %>%
                        ungroup() %>%
                        distinct() %>%
                        group_by(salt) %>%
                        dplyr::summarise(prop = mean(prop_salt_yr)) %>%
                        ungroup() %>%
                        mutate(type = 'salt') %>%
                        rename(class = salt)
)

wst_dat = wst_env_dat %>%
  dplyr::select(-month) %>%
  left_join(smolt_count %>%
  dplyr::select(year, nor_sthd)) %>%
  left_join(ad_count %>%
  dplyr::select(year, nor_wsthd, wsthd_total_escapement)) %>%
  #adjust covs to years
  mutate(esc_adj = ifelse(is.na(lag(wsthd_total_escapement,2)), lag(wsthd_total_escapement,3) * filter(wst_props, type == 'age' & class == 2)$prop,
                          lag(wsthd_total_escapement,2)*filter(wst_props, type == 'age' & class == 2)$prop) +
           lag(wsthd_total_escapement,3) * filter(wst_props, type == 'age' & class == 3)$prop+
           lag(wsthd_total_escapement,4) * filter(wst_props, type == 'age' & class == 4)$prop+
           lag(wsthd_total_escapement,5) * filter(wst_props, type == 'age' & class == 5)$prop+
           ifelse(is.na(lag(wsthd_total_escapement,6)), lag(wsthd_total_escapement,5) * filter(wst_props, type == 'age' & class == 6)$prop,
                  lag(wsthd_total_escapement, 6) * filter(wst_props, type == 'age' & class == 6)$prop),
         smolt_adj = ifelse(is.na(lag(nor_sthd,1)),
                            lag(nor_sthd,2) * filter(wst_props, type == 'salt' & class == 1)$prop,
                            lag(nor_sthd,1) * filter(wst_props, type == 'salt' & class == 1)$prop)+
           lag(nor_sthd,2) * filter(wst_props, type == 'salt' & class == 2)$prop+
           lag(nor_sthd,3) * filter(wst_props, type == 'salt' & class == 3)$prop,
         # spill_adj = lag(mean_spill, 1) * filter(wst_props, type == 'salt' & class == 1)$prop+
         #   lag(mean_spill, 2) * filter(wst_props, type == 'salt' & class == 2)$prop+
         #   lag(mean_spill, 3) * filter(wst_props, type == 'salt' & class == 3)$prop+
         #   lag(mean_spill, 4) * filter(wst_props, type == 'salt' & class == 4)$prop,
         min_flow_adj = lag(min_flow_yr, 2) * filter(wst_props, type == 'age' & class == 2)$prop+
           lag(min_flow_yr, 3) * filter(wst_props, type == 'age' & class == 3)$prop+
           lag(min_flow_yr, 4) * filter(wst_props, type == 'age' & class == 4)$prop+
           lag(min_flow_yr, 5) * filter(wst_props, type == 'age' & class == 5)$prop+
           ifelse(is.na(lag(min_flow_yr,6)), lag(min_flow_yr,5) * filter(wst_props, type == 'age' & class == 6)$prop,
                  lag(min_flow_yr, 6) * filter(wst_props, type == 'age' & class == 6)$prop),
         # temp_out_adj = lag(temp_out, 1) * filter(wst_props, type == 'salt' & class == 1)$prop+
         #   lag(temp_out, 2) * filter(wst_props, type == 'salt' & class == 2)$prop+
         #   lag(temp_out, 3) * filter(wst_props, type == 'salt' & class == 3)$prop+
         #   lag(temp_out, 4) * filter(wst_props, type == 'salt' & class == 4)$prop,
         npgo_adj = lag(npgo, 1) * filter(wst_props, type == 'salt' & class == 1)$prop+
           lag(npgo, 2) * filter(wst_props, type == 'salt' & class == 2)$prop+
           lag(npgo, 3) * filter(wst_props, type == 'salt' & class == 3)$prop+
           lag(npgo, 4) * filter(wst_props, type == 'salt' & class == 4)$prop) %>%
  mutate(esc_std = (esc_adj - mean(esc_adj, na.rm = T))/sd(esc_adj, na.rm = T),
         # spill_std = (spill_adj - mean(spill_adj, na.rm = T))/sd(spill_adj, na.rm = T),
         min_flow_std = (min_flow_adj - mean(min_flow_adj, na.rm = T))/sd(min_flow_adj, na.rm = T),
         npgo_std = (npgo_adj - mean(npgo_adj, na.rm = T))/sd(npgo_adj, na.rm = T),
         # temp_in_std = (temp_in - mean(temp_in, na.rm = T))/sd(temp_in, na.rm = T),
         # temp_out_std = (temp_out_adj - mean(temp_out_adj, na.rm = T))/sd(temp_out_adj, na.rm = T),
         esc_smoltmod_adj = ifelse(is.na(lag(wsthd_total_escapement, 1)), lag(wsthd_total_escapement,2) * filter(wst_props, type == 'fresh' & class == 1)$prop,
                                   lag(wsthd_total_escapement, 2)*filter(wst_props, type == 'fresh' & class == 1)$prop)+
           lag(wsthd_total_escapement, 3) * filter(wst_props, type == 'fresh' & class == 2)$prop+
           lag(wsthd_total_escapement, 4) * filter(wst_props, type == 'fresh' & class == 3)$prop+
           lag(wsthd_total_escapement, 5) * filter(wst_props, type == 'fresh' & class == 4)$prop,
         min_flow_smoltmod_adj = lag(min_flow_yr,1) * filter(wst_props, type == 'fresh' & class == 2)$prop+
           lag(min_flow_yr,2) * filter(wst_props, type == 'fresh' & class == 3)$prop+
           lag(min_flow_yr,3) * filter(wst_props, type == 'fresh' & class == 4)$prop
  )

```

```{r NOR-wsthd}
if(!file.exists(paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_wsthd_mod.rda"))){
#run model
mod_wst = brm(nor_wsthd ~ 0 + smolt_adj + min_flow_adj  +  npgo_adj, data = wst_dat)

save(mod_wst, file = paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_wsthd_mod.rda"))
}else{load(paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_wsthd_mod.rda")) 
  
}
wst_pred = posterior_predict(mod_wst, filter(wst_dat, year == prediction_year))
wst_int = predictive_interval(wst_pred)
```

```{r HOR-wsthd}
hwst_props = read_excel('data input/Abundance/AgeData.xlsx',
                        sheet = 'HOR WSTHD') %>%
  janitor::clean_names() %>%
  pivot_longer(2:last_col(1)) %>%
  dplyr::mutate(salt = substr(name,2,2)) %>%
  group_by(salt) %>%
  dplyr::summarise(prop =  sum(value)/sum(total)) %>%
  ungroup() #%>%
  # mutate(type = 'salt') %>%
  # rename(class = salt)

hwst_dat = npgo %>%
  filter(month == 5 | is.na(month)) %>%
  left_join(smolt_count %>%
  dplyr::select(year, hor_wsthd) %>%
  dplyr::rename(hor_smolt = hor_wsthd)) %>%
  left_join(ad_count %>%
              dplyr::select(year, hor_wsthd)) %>%
  mutate(smolt_adj = lag(hor_smolt, 1) * filter(hwst_props, salt == '1')$prop +
           lag(hor_smolt, 2) * filter(hwst_props, salt == '2')$prop+
           lag(hor_smolt, 3) * filter(hwst_props, salt == '3')$prop+
           lag(hor_smolt, 4) * filter(hwst_props, salt == '4')$prop,
         npgo_adj = lag(npgo, 1) * filter(hwst_props, salt == '1')$prop +
           lag(npgo, 2) * filter(hwst_props, salt == '2')$prop +
           lag(npgo, 3) * filter(hwst_props, salt == '3')$prop
  )
if(!file.exists(paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_wsthd_mod.rda"))){
#Model
mod_hwst = brm(hor_wsthd ~ 0 + smolt_adj + npgo_adj, data = hwst_dat)

save(mod_hwst, file = paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_wsthd_mod.rda"))
}else{load(paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_wsthd_mod.rda"))
}

hwst_pred = posterior_predict(mod_hwst, filter(hwst_dat, year == prediction_year))
hwst_int = predictive_interval(hwst_pred)
```

```{r SSTHD}
sst_props = read_excel('data input/Abundance/AgeData.xlsx',
                       sheet = 'NOR SSTHD') %>%
  janitor::clean_names() %>%
  pivot_longer(2:last_col(1)) %>%
  dplyr::mutate(salt = substr(name,2,2)) %>%
  group_by(salt) %>%
  dplyr::summarise(prop =  sum(value)/sum(total)) %>%
  ungroup() %>%
  mutate(type = 'salt') %>%
  rename(class = salt)
  


sst_dat = npgo %>%
  filter(month == 5 | is.na(month)) %>%
  left_join(tucker_flow) %>%
  left_join(ad_count %>% 
              dplyr::select(year, ssthd, ssthd_bon, ssthd_dalles)) %>%
  left_join(smolt_count %>%
              dplyr::select(year, nor_sthd)) %>%
  mutate(damcount = ssthd_bon - ssthd_dalles,
         damcount_adj = lag(damcount,1),
         smolt_adj = lag(nor_sthd, 1) * filter(sst_props, class == 1)$prop+
           lag(nor_sthd, 2) * filter(sst_props, class == 2)$prop+
           lag(nor_sthd, 3) * filter(sst_props, class == 3)$prop,
         npgo_adj = lag(npgo,1) * filter(sst_props, class == 1)$prop+
           lag(npgo, 2) * filter(sst_props, class == 2)$prop+
           lag(npgo, 3) * filter(sst_props, class == 3)$prop,
         min_flow_adj = lag(min_flow_yr,2) * filter(sst_props, class == 1)$prop+
           lag(min_flow_yr,3) * filter(sst_props, class == 2)$prop+
           lag(min_flow_yr,4) * filter(sst_props, class == 3)$prop)
  

if(!file.exists(paste0(here::here(),"/R/Model objects/",prediction_year,"/ssthd_mod.rda"))){
#run model
mod_sst = brm(ssthd ~ 0 + damcount_adj + npgo_adj + min_flow_adj, data = sst_dat)

save(mod_sst, file = paste0(here::here(),"/R/Model objects/",prediction_year,"/ssthd_mod.rda"))
}else{load(paste0(here::here(),"/R/Model objects/",prediction_year,"/ssthd_mod.rda"))
}
#predictions
sst_pred = posterior_predict(mod_sst, filter(sst_dat, year == prediction_year))
sst_int = predictive_interval(sst_pred)
```

```{r HOR-spch}
hsc_ages = read_excel('data input/Abundance/AgeData.xlsx',
                      sheet = 'HOR SPCH') %>%
  janitor::clean_names() %>%
  pivot_longer(2:last_col(1)) %>%
  dplyr::mutate(salt = substr(name,2,2),
                salt_prop = value/total)

hsc_props = left_join(hsc_ages %>% group_by(salt) %>%
                        dplyr::summarise(prop_yr = mean(salt_prop)) %>%
                        ungroup(),
                      hsc_ages %>% group_by(salt) %>%
                        dplyr::summarise(prop_tot = sum(value)/sum(total)) %>%
                        ungroup()
                      
)

#Get data together
#abundance
hsc_count = ad_count %>%
  dplyr::select(year, hor_spch, hor_spch_jack) %>%
  left_join(smolt_count %>%
              rename(hor_spch_smolt = hor_spch) %>%
              dplyr::select(year, hor_spch_smolt))

#env
hsc_env =  npgo %>% 
  filter(month == 5 | is.na(month)) %>%
  dplyr::select(year,npgo)
  # left_join(bon %>%
  # filter(hsc_out == 'yes') %>%
  # group_by(year) %>%
  # dplyr::summarise(mean_spill = mean(spill_kcfs, na.rm = T),
  #                  temp_out = mean(temperature_c, na.rm = T)) %>%
  # ungroup())

#join together, offset by ages (for both adult and jack model)
hsc_dat = hsc_env %>%
  left_join(hsc_count) %>%
  mutate(smolt_jack_adj = lag(hor_spch_smolt,3),
         smolt_ad_adj_tot = lag(hor_spch_smolt,4)*filter(hsc_props, salt == 3)$prop_tot +
           lag(hor_spch_smolt,5)*filter(hsc_props,salt==3)$prop_tot,
         npgo_jack_adj = lag(npgo,1),
         npgo_ad_adj_tot = lag(npgo,2)*filter(hsc_props, salt == 2)$prop_tot +
           lag(npgo,3)*filter(hsc_props,salt == 3)$prop_tot,
         # spill_jack_adj = lag(mean_spill, 1),
         # spill_ad_adj_tot = lag(mean_spill,2)*filter(hsc_props, salt == 2)$prop_tot +
         #   lag(mean_spill,3)*filter(hsc_props,salt == 3)$prop_tot,
         prior_jack_adj_tot = lag(smolt_jack_adj,1)*filter(hsc_props, salt == 2)$prop_tot+
           lag(smolt_jack_adj,2)*filter(hsc_props, salt == 3)$prop_tot,
         prior_returns_adj_tot = lag(smolt_jack_adj,1)*filter(hsc_props, salt == 2)$prop_tot+
           lag(smolt_jack_adj,2)*filter(hsc_props, salt == 3)$prop_tot+
           lag(hor_spch,1)*filter(hsc_props,salt == 3)$prop_tot
  )
if(!file.exists(paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_spch_mods.rda"))){
#run model
#adults
mod_hsc_ad = brm(hor_spch ~ 0 + smolt_ad_adj_tot + npgo_ad_adj_tot, data = hsc_dat)


#jacks
mod_hsc_jack = brm(hor_spch_jack ~ 0 + smolt_jack_adj + npgo_jack_adj, data = hsc_dat, iter = 4000)
# hsc_jack_lm = lm(hor_spch_jack ~ 0 + smolt_jack_adj + npgo_jack_adj, data = hsc_dat)
save(mod_hsc_ad, mod_hsc_jack, file = paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_spch_mods.rda"))
}else{load(paste0(here::here(),"/R/Model objects/",prediction_year,"/hor_spch_mods.rda"))
}

hsc_ad_pred = posterior_predict(mod_hsc_ad, filter(hsc_dat, year == prediction_year))
hsc_ad_int = predictive_interval(hsc_ad_pred)

hsc_jack_pred = posterior_predict(mod_hsc_jack, filter(hsc_dat, year == prediction_year))
hsc_jack_int = predictive_interval(hsc_jack_pred)

```

```{r NOR-spch}
nsc_dat = npgo %>%
  filter(month == 9 | is.na(month)) %>%
  left_join(tucker_flow) %>%
  left_join(ad_count %>%
  dplyr::select(year, nor_spch, nor_spch_jack, spch_bon, spch_dalles)) %>%
  mutate(spch_damcount = spch_bon - spch_dalles,
         spch_dam_adj = lag(spch_damcount, 4) * filter(hsc_props, salt == 2)$prop_tot+
           lag(spch_damcount, 5) * filter(hsc_props, salt == 3)$prop_tot,
         jack_count_adj = lag(nor_spch_jack,1) * filter(hsc_props, salt == 2)$prop_tot+
           lag(nor_spch_jack, 2) * filter(hsc_props, salt == 3)$prop_tot,
         min_flow_adj = lag(min_flow_yr, 3) * filter(hsc_props, salt == 2)$prop_tot+
           lag(min_flow_yr, 4) * filter(hsc_props, salt == 3)$prop_tot,
         npgo_adj = lag(npgo, 2) * filter(hsc_props, salt == 2)$prop_tot+
           lag(npgo, 3) * filter(hsc_props, salt == 3)$prop_tot,
         spch_dam_jack_adj = lag(spch_damcount, 3),
         min_flow_jack_adj = lag(min_flow_yr, 2),
         npgo_jack_adj = lag(npgo, 1)
         )

if(!file.exists(paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_spch_mods.rda"))){
#run models

mod_nsc_ad = brm(nor_spch ~ 0 + spch_dam_adj + min_flow_adj, data = nsc_dat)

mod_nsc_jack = brm(nor_spch_jack ~ 0 + spch_dam_jack_adj + npgo_jack_adj, data = nsc_dat)

save(mod_nsc_ad, mod_nsc_jack, file = paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_spch_mods.rda"))
}else{load(paste0(here::here(),"/R/Model objects/",prediction_year,"/nor_spch_mods.rda"))
}

nsc_ad_pred = posterior_predict(mod_nsc_ad, filter(nsc_dat, year == prediction_year))
nsc_ad_int = predictive_interval(nsc_ad_pred)

nsc_jack_pred = posterior_predict(mod_nsc_jack, filter(nsc_dat, year == prediction_year))
nsc_jack_int = predictive_interval(nsc_jack_pred)
```


## Forecasts

Below are the forecasts for `r prettyNum(prediction_year)`  
```{r forecast-results-table, results = "hold"}

tibble(run = c("NOR winter steelhead", "HOR winter steelhead", "NOR summer steelhead", "NOR spring Chinook adults", "NOR spring Chinook jacks", "HOR spring Chinook adults", "HOR spring Chinook jacks"),
                      estimate = c(median(wst_pred), median(hwst_pred), median(sst_pred) ,median(nsc_ad_pred), median(nsc_jack_pred), median(hsc_ad_pred), median(hsc_jack_pred)),
                      ci_lower = c(wst_int[1], hwst_int[1], sst_int[1], nsc_ad_int[1], nsc_jack_int[1], hsc_ad_int[1], hsc_jack_int[1]),
                      ci_upper = c(wst_int[2], hwst_int[2], sst_int[2], nsc_ad_int[2], nsc_jack_int[2], hsc_ad_int[2], hsc_jack_int[2])) %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower),
         estimate = ifelse(estimate < 0, 0, estimate),
         ci_upper = ifelse(ci_upper < 0, 0, ci_upper)) %>%
  flextable() %>%
  set_table_properties(layout = "autofit") %>%
  set_header_labels(values = list(run = "Run",
                                  estimate = "Prediction",
                                  ci_lower = "90% PI, lower",
                                  ci_upper = "90% PI, upper")) %>%
  colformat_double(digits = 0) %>%
  theme_vanilla()%>% 
  align(align ='center', part = 'all') %>% 
  align(j = 1, align ='left', part = 'all') 
  # kable(booktabs = T,
  #       digits = 0,
  #       align = "lccc",
  #       format.args = list(big.mark = ","),
  #       col.names = c("Run", "Prediction", "90% PI, lower", "90% PI, upper")) %>%
  # kable_styling(full_width = F,
  #               position = "center",
  #               bootstrap_options = c("striped", "condensed"))

```

## Prediction Figures  

```{r function-for-obs_pred-plot}
plot_obs_pred = function(mod = NULL,
                         data = NULL,
                         resp = NULL,
                         predictor = NULL,
                         prediction_year = prediction_year,
                         ylab = NULL){
  
  resp = enquo(arg = resp)
  predictor = enquo(arg = predictor)

  fit_pred = posterior_epred(mod, filter(data,!is.na(!!predictor) &
                                               !is.na(!!resp)))
  
  fit_pred_sum = tibble(year = filter(data, !is.na(!!predictor) & !is.na(!!resp))$year,
                        med = apply(fit_pred,2,median),
                        q.025 = apply(fit_pred, 2,function(x) quantile(x,0.025)),
                        q.975 = apply(fit_pred, 2,function(x) quantile(x, 0.975)),
                        type = "Fitted")
  
  out_pred = posterior_predict(mod, filter(data, !is.na(!!predictor) &
                                               is.na(!!resp)))

  out_pred_sum = tibble(year = filter(data, !is.na(!!predictor) & is.na(!!resp))$year,
                        med = apply(out_pred,2,median),
                        q.025 = apply(out_pred, 2,function(x) quantile(x,0.025)),
                        q.975 = apply(out_pred, 2,function(x) quantile(x, 0.975)),
                        type = "Predicted")

  obs = dplyr::select(data, year, !!resp) %>%
    mutate(type = "Observed") %>%
    rename(med = !!resp)

  plot = bind_rows(fit_pred_sum, out_pred_sum, obs) %>%
    drop_na(med) %>%
    mutate(ifelse(q.025 < 0, 0, q.025)) %>%
    ggplot()+
    geom_errorbar(aes(x = year, ymin = q.025, ymax = q.975), alpha = .5, width = 0.75)+
    #scale_linetype_manual(values = c("Fitted" = 'solid',"Predicted" = 'dotdash'))+
    geom_point(aes(x = year, y = med, fill = type, shape = type, color = type), color = 'black')+
    scale_color_manual(values = c("Fitted" = 'black',"Observed" = 'black',"Predicted" = 'red'))+
    scale_shape_manual(values = c("Fitted" = 21,"Observed" = 21,"Predicted" = 21))+
    scale_fill_manual(values = c("Fitted"='black',"Observed"='white',"Predicted"='red'))+
    theme_bw()+
    theme(legend.position = 'top',
        legend.title = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_text(color = 'black'),
        text = element_text(family = 'serif')
        )+
    guides(linetype = 'none', color = 'none')+
    labs(x = "Year", y = ylab)
    
  
  return(plot)
}

```
### NOR Winter Steelhead  
```{r NOR-wsthd-results, results = "hold"}
#Obs v pred
obs_pred = plot_obs_pred(mod = mod_wst, data = wst_dat, resp = nor_wsthd, predictor = smolt_adj, prediction_year = prediction_year, ylab = "Returns")

obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/NOR_wsthd_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()
```

### HOR Winter Steelhead  
```{r HOR-wsthd-results, results = "hold"}
obs_pred = plot_obs_pred(mod = mod_hwst, data = hwst_dat, resp = hor_wsthd, predictor = smolt_adj, prediction_year = prediction_year, ylab = "Returns")
obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/HOR_wsthd_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()
```

### NOR Summer Steelhead  
```{r SSTHD-results, results = "hold"}
#obs vs. pred
obs_pred = plot_obs_pred(mod = mod_sst, data = sst_dat, resp = ssthd, predictor = damcount_adj, prediction_year = prediction_year, ylab = "Returns")
obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/NOR_ssthd_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()
```

### NOR Spring Chinook

Jack model:

```{r nsc-jack-result, results = "hold"}
#Obs v pred
obs_pred = plot_obs_pred(mod = mod_nsc_jack, data = nsc_dat, resp = nor_spch_jack, predictor = spch_dam_jack_adj, prediction_year = prediction_year, ylab = "Jack Returns")
obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/NOR_spch_jack_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()

```

Adult model:

```{r nsc-adult-results, results = "hold"}
#Obs v pred
obs_pred = plot_obs_pred(mod = mod_nsc_ad, data = nsc_dat, resp = nor_spch, predictor = spch_dam_adj, prediction_year = prediction_year, ylab = "Adult Returns")
obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/NOR_spch_adult_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()
```

### HOR Spring Chinook

Jack model:

```{r HOR-spch-jack-results, results = "hold"}
#Obs v pred
obs_pred = plot_obs_pred(mod = mod_hsc_jack, data = hsc_dat, resp = hor_spch_jack, predictor = smolt_jack_adj, prediction_year = prediction_year, ylab = "Jack Returns")
obs_pred

tiff(filename = paste0("report output/",prediction_year,"/figures/HOR_spch_jack_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()
```

Adult model:

```{r HOR-spch-ad-results, results = "hold"}
#Obs v pred
obs_pred = plot_obs_pred(mod = mod_hsc_ad, data = hsc_dat, resp = hor_spch, predictor = smolt_ad_adj_tot, prediction_year = prediction_year, ylab = "Adult Returns")
obs_pred
tiff(filename = paste0("report output/",prediction_year,"/figures/HOR_spch_adult_ObsPred.tiff"),
                       res = 1000,
                       compression = 'lzw',
                       width = 6.5,
                       height = 3.5,
                       units = 'in')
obs_pred
x = dev.off()

```

## Model Information
### NOR Winter Steelhead  
```{r NOR-wsthd-mod-info, results = "hold"}
summary(mod_wst)
```
### HOR Winter Steelhead  
```{r HOR-wsthd-mod-info, results = "hold"}
#mod summary
summary(mod_hwst)
```

### NOR Summer Steelhead  
```{r SSTHD-mod-info, results = "hold"}
#summaries
summary(mod_sst)
```

### NOR Spring Chinook

Jack model:

```{r nsc-jack-mod-info, results = "hold"}
summary(mod_nsc_jack)
```

Adult model:

```{r nsc-adult-mod-info, results = "hold"}
summary(mod_nsc_ad)
```

### HOR Spring Chinook

Jack model:

```{r HOR-spch-jack-mod-info, results = "hold"}
summary(mod_hsc_jack)
```

Adult model:

```{r HOR-spch-ad-mod-info, results = "hold"}
summary(mod_hsc_ad)
```
